### 2015-05-13 evaluation.tex
update in evaluation text

\medskip\noindent\textbf{Granularity of Context-Switches }
%
Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks, while Figure~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. All reported times, in seconds, are averages over three runs. \corral was given a time budget of 10 hours (T.O. denotes timeout), and we considered context-switch bounds (csb) of 2, 5 and 9, respectively. By default, \corral instruments context-switches (i.e. \texttt{yield} statements) in \ADComment{instead of ``in'' can we say either ``before'' or ``after'' (not sure which is accurate)} all visible operations (denoted \yieldall). \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{corral}).

>>>>

\medskip\noindent\textbf{Granularity of Context-Switches }
%
Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks, while Figure~\ref{fig:plot} plots the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. All reported times, in seconds, are averages over three runs. \corral was given a time budget of 10 hours (T.O. denotes timeout), and we considered context-switch bounds (csb) of 2, 5 and 9, respectively. When we run standalone \corral we enable the \yieldall instrumentation, which instruments context-switches (i.e. \texttt{yield} statements) after all visible operations. \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{corral}).
